---
title: "EPS vs Stock Sell Price"
author: "Venkat Gopalakrishnan"
date: "3/4/2017"
output: html_document
---

```{r, warning=FALSE, include=FALSE}

library("TSA")
library("forecast")
library("tseries")
library("zoo")
library("lubridate")
library("bsts")
library("dplyr")
library("ggplot2")

```



```{r warning=FALSE}

# functions definition

ggplotRegression <- function (fit) {

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}


```


```{r warning=FALSE}

epsData <- read.csv("/Users/VK/Desktop/UChicago/TimeSeries/Final Project/Data/eps/PCLN.csv", header=TRUE, sep = ",")


epsTS <- ts(epsData$EPS, start = c(2007,1), end=c(2016,4), frequency = 4)
HighPriceTS <- ts(epsData$HighStockPrice, start = c(2007,1), end=c(2016,4), frequency = 4)

plot(stl(epsTS, "periodic"), main="EPS")
plot(stl(HighPriceTS, "periodic"), main="Stock")


# there is a clear (upward) trend and seasonality.

```



# Model - 1 (Seasonal and Sequential models with Historical EPS data to forecast EPS)


```{r warning=FALSE}

# model by season - quarter by quarter

q1.forecastEps <- forecast(auto.arima(subset(epsTS, quarter = 1)),h=4)
q2.forecastEps <- forecast(auto.arima(subset(epsTS, quarter = 2)),h=4)
q3.forecastEps <- forecast(auto.arima(subset(epsTS, quarter = 3)),h=4)
q4.forecastEps <- forecast(auto.arima(subset(epsTS, quarter = 4)),h=4)

plot(q1.forecastEps)
plot(q2.forecastEps)
plot(q3.forecastEps)
plot(q4.forecastEps)

# model by sequence

myarima.epsTS <- auto.arima(epsTS)
summary(myarima.epsTS)
acf(myarima.epsTS$residuals)

forecast.arimaEps <- forecast(myarima.epsTS,h=8)
plot(q1.forecastEps, main="ARIMA - Seasonal (Q1)")


q1.forecastEps

consTS <- ts(epsData$Cons., start = c(2007,1), end=c(2016,4), frequency = 4)


plot(forecast.arimaEps, main="ARIMA - Continuous")
q1Arima <- auto.arima(subset(epsTS, quarter = 1), xreg= subset(consTS, quarter = 1))
q2Arima <- auto.arima(subset(epsTS, quarter = 2), xreg= subset(consTS, quarter = 2))
q3Arima <- auto.arima(subset(epsTS, quarter = 3), xreg= subset(consTS, quarter = 3))
q4Arima <- auto.arima(subset(epsTS, quarter = 4), xreg= subset(consTS, quarter = 4))
q2.forecastEps <- forecast(q2Arima, h=1, xreg = forecast(auto.arima(subset(consTS, quarter = 2)), h=1)$mean)
q3.forecastEps <- forecast(q3Arima, h=1, xreg = forecast(auto.arima(subset(consTS, quarter = 3)), h=1)$mean)
q4.forecastEps <- forecast(q4Arima, h=1, xreg = forecast(auto.arima(subset(consTS, quarter = 4)), h=1)$mean)
q1.forecastEps <- forecast(q1Arima, h=1, xreg = forecast(auto.arima(subset(consTS, quarter = 1)), h=1)$mean)

plot(q1.forecastEps, main="Q1 Forecast")
plot(q2.forecastEps, main="Q2 Forecast")
plot(q3.forecastEps, main="Q3 Forecast")
plot(q4.forecastEps, main="Q4 Forecast")


```

# EPS Prediction Model - 1.2, Linear Regression: Historical Consensus data vs Historical EPS to predict the EPS

```{r warning=FALSE}

lm.conVsEps <- lm(EPS ~ Cons., data = epsData)
summary(lm.conVsEps)
ggplotRegression(lm.conVsEps)

```

# Highest (stock) sell price Prediction Model 2.1 - (Linear Regression - Predict Highest stock price on the day of earnings based on EPS)

```{r warning=FALSE}


lm.EpsVsHighPrice <- lm(HighStockPrice ~ EPS, data = epsData)
summary(lm.EpsVsHighPrice)
ggplotRegression(lm.EpsVsHighPrice)
plot(lm.EpsVsHighPrice$residuals)

```



# Highest (stock) sell price Prediction Model 2.2 - (ARIMA model based on historical highest stock prices on the prior earnings day)

```{r warning=FALSE}

myarima.StockPriceTS <- auto.arima(HighPriceTS)
summary(myarima.StockPriceTS)
forecast.arimaStockPrice <- forecast(myarima.StockPriceTS,h=4)

# ARIMA with regression

myarima.xreg.StockPriceTS <- auto.arima(HighPriceTS, xreg = epsTS)

xreg.ar.forecaststock <- forecast(myarima.xreg.StockPriceTS, h=8, xreg = forecast(auto.arima(epsTS), h=8)$mean)

plot(forecast(xreg.ar.forecaststock))


```


# Model 3 - GARCH Model/Plan B model (If Model 1 and 2 fails, if we fail to predict Highest Stock Price from ARIMA and Regression models, then Predict Highest price from seeing how volatile it was on prior earnings announcement)

```{r warning=FALSE}

# the earnings was on 27th after close, the next immediate trading day was 28th Feb. We will find how volatile it was for that surprise percentage

pcln.10yrs.high <- get.hist.quote(instrument = "NFLX", 
                                  start = "2016-02-28", end = "2017-03-07", 
                                  quote="High", provider = "yahoo", 
                                  compression = "d", retclass = "zoo")


highprice.arima <- auto.arima(pcln.10yrs.high)
forecast(highprice.arima,h=30)

#find monthly compound returns
log.return.pcln <- diff(log(pcln.10yrs.high)) * 100
plot(log.return.pcln)

#fit and check if we have arch effect )

check.arch.fit <- auto.arima(log.return.pcln, trace=TRUE)
Box.test(check.arch.fit$residuals^2,type = "Ljung-Box", lag=12)

# develop garch spec


plot(pcln.10yrs.high)
```


```
# References:
http://www.cnbc.com/2015/04/27/simple-strategy-earns-massive-profits-on-earnings.html
https://www.thestreet.com/slideshow/13525752/1/10-most-volatile-s-amp-p-500-stocks-on-earnings-day.html
https://optionalpha.com/proven-ways-to-profit-from-a-stocks-earnings-release-using-these-3-option-strategies-16441.html
```
